### 2019-12-12 README.Rmd
updated docs

To download, develop, and install:

1. Be sure to have `devtools` installed.
1. Use RStudio to create a local copy in `~/tmp` based on https://github.com/jlucasmckay/MSbalance
1. Edit vignettes/msBalance.Rmd and R files in R/.
1. Stage changed files, commit, and push changes with the git panel.
1. `devtools::install_github("jlucasmckay/msBalance", build_vignettes = TRUE)`
1. `vignette("msBalance")`

>>>>

1. Be sure to have `devtools` installed.
1. Use RStudio to create a local copy in `~/tmp` based on https://github.com/jlucasmckay/msBalance
    1. In RStudio, start a new Project: `File > New Project > Version Control > Git`
    1. In the “repository URL” paste: https://github.com/jlucasmckay/msBalance
    1. On OS X, make under `tmp`
    1. Click “Create Project” to create a new directory, which will be:
        * A directory/folder under `tmp`
        * A Git repository, linked to the remote GitHub repository
        * An RStudio Project
    1. If there are files that need to be added to the remote, they can be placed in this folder or dragged / dropped into the GitHub interface.
1. Edit vignettes/msBalance.Rmd and R files in R/.
1. Stage changed files, commit, and push changes with the git panel.

### Installing from GitHub for use
1. `devtools::install_github("jlucasmckay/msBalance", build_vignettes = TRUE)`
1. `vignette("msBalance")`
